---
title: "assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Different People Have Different Sources of Happiness

Different people derive their happiness from different sources. By investigating these sources, we can fundamentally understand the key to enhancing happiness. We are fortunate to have access to the HappyDB database, which contains a wealth of workers' descriptions of their sources of happiness. By examining this dataset and identifying the diverse sources of happiness, we can assist factories in devising targeted incentive plans to boost happiness and, consequently, productivity. In this notebook, we employ R notebook for data mining and ultimately display the various sources of happiness for different people via word clouds.


### Step 0 - Load all the required libraries

```{r load libraries, warning=FALSE, message=FALSE}

library(dplyr)
library(ggplot2)
library(reshape2)
library(stringr)
library(wordcloud2)
library(shiny)
library(htmlwidgets)
library(webshot)
library(png)
library(grid)
source('../lib/wordcloud.R')
# The following install_phantomjs() should be comment out when knit a html
webshot::install_phantomjs()
```


### Step 1 - Load the data from HappyDB and Data preprocessing
Dataset using: HappyDB, HappyDB is a corpus of 100,000+ crowd-sourced happy moments. The goal of the corpus is to advance the state of the art of understanding the causes of happiness that can be gleaned from text. 

```{r load data, warning=FALSE, message=FALSE}
cleaned_hm <- read.csv("../data/cleaned_hm.csv")
demographics <- read.csv("../data/demographic.csv")
```

Combine both the datasets and keep only the required columns

```{r combining data, warning=FALSE, message=FALSE}
merged_data <- merge(cleaned_hm, demographics, by = "wid", all.y = TRUE)
selected_data <- merged_data[, c("wid", "hmid", "predicted_category", "age", "country", "gender", "marital", "parenthood")]
```

Data preprocessing
Clean the NA values:

```{r data null clean, warning=FALSE, message=FALSE}
prev_na <- sapply(selected_data, function(y) sum(length(which(is.na(y)))))
print("NA Values:")
print(prev_na[prev_na > 0])
selected_data <- na.omit(selected_data)
```
We now have a dataset devoid of any empty values. The next step is to remove non-majority categories from the dataset. This is not because these categories are unimportant, but because their numbers are too small to be representative.
```{r data preprocessing, warning=FALSE, message=FALSE}  
selected_data <- subset(selected_data, gender == "f" | gender == "m")
selected_data <- subset(selected_data, parenthood == "n" | parenthood == "y")
selected_data$marital <- ifelse(selected_data$marital == "married", "married", "not-married")
selected_data$age <- as.numeric(selected_data$age)
selected_data <- subset(selected_data, age >= 18 & age <= 100)
```

### Step 2 - Data Exploration:  

At this stage, we will explore the data, identify its unique characteristics, and analyze its median. 
The code below will generate the number of data entries from workers in different countries. The chart reveals that the data from USA workers greatly exceeds the total from other countries, suggesting that our analysis might not be representative of other nations, nor can it explore the differences between them. Therefore, this analysis will focus solely on data from American workers.

```{r workers countries distribution, warning=FALSE, message=FALSE}
top_countries <- selected_data %>%
  count(country) %>%
  arrange(desc(n)) %>%
  head(5)

ggplot(top_countries, aes(x=reorder(country, n), y=n)) +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=n), vjust=-0.5, size=4) +
  labs(x="Country", y="Frequency",title = paste("Total data: ", sum(top_countries$n)))

selected_data <- subset(selected_data, country == "USA")
```
Here, we have produced five charts. 
The first three represent the proportion of data pertaining to different genders, marital statuses, and parenthood statuses. 
The fourth chart represents the tags of the workers' sources of happiness. From the chart, we can see that most people find happiness in Affection and Achievement. However, these tags are not detailed enough to analyze workers' sources of happiness, so we need to rely on their specific sentences for further analysis. 
The fifth chart displays the age distribution of the surveyed workers. From this age chart, we can see that the majority of ages range from 20 (actually 18) to 60, so we will limit our subsequent analysis to this age range.

  
```{r Gender Marital Parenthood Pie Chart, warning=FALSE, message=FALSE}  
ggplot(selected_data, aes(x="", fill=gender)) +
  geom_bar(width = 1) +
  coord_polar("y", start=0) +
  theme_void()
ggplot(selected_data, aes(x="", fill=marital)) +
  geom_bar(width = 1) +
  coord_polar("y", start=0) +
  theme_void()
ggplot(selected_data, aes(x="", fill=parenthood)) +
  geom_bar(width = 1) +
  coord_polar("y", start=0) +
  theme_void()
category <- selected_data %>%
  count(predicted_category) %>%
  arrange(desc(n))
ggplot(category, aes(x=reorder(predicted_category, n), y=n)) +
  geom_bar(stat="identity", fill="steelblue") +
  geom_text(aes(label=n), vjust=-0.3, size=3.3) +
  labs(x="Happiness Category", y="Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
  
  
  
```{r Age Group Filter, warning=FALSE, message=FALSE}  
selected_data$age <- as.numeric(selected_data$age)
selected_data <- selected_data %>% filter(age >= 1 & age <= 100)
selected_data$age_group <- cut(selected_data$age, breaks = seq(0, 100, by = 5))
levels(selected_data$age_group) <- seq(0, 95, by = 5)
ggplot(selected_data, aes(x=age_group)) +
  geom_bar(fill = "steelblue") +
  labs(x="Age Group", y="Count",title = paste("Percentage of rows where age is between 15 and 30: ", round(selected_data%>% filter(age >= 18, age <= 30) %>% nrow() / nrow(selected_data) * 100, 2), "%"))+
  theme_minimal()
```
  
The next chart also roughly categorizes sources of happiness to see if young people (under 30) and middle-aged people (30 and above) have different sources of happiness. However, the chart does not reveal any significant differences between them. The only noticeable difference is that middle-aged people place more emphasis on affection-based happiness, while young people may feel slightly less happiness from achievements.

```{r teen vs mid, warning=FALSE, message=FALSE }
teen = selected_data%>% filter(age >= 18, age <= 30)
mid  = selected_data%>% filter(age >= 30, age <= 60)
teen$age_group <- "18-30"
mid$age_group <- "30-60"
df <- rbind(teen, mid)
df <- df %>%
  group_by(age_group, predicted_category) %>%
  summarise(count = n())
ggplot(df, aes(x=predicted_category, y=count, fill=age_group)) +
  geom_bar(stat="identity", position="dodge") +
  scale_fill_manual(values=c("18-30"="red", "30-60"="steelblue")) +
  theme_minimal() +
  labs(x="Predicted Category", y="Count", fill="Age Group") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12))
```
  
### Step 4 - Word Cloud
To further explore the different sources of happiness for people with different tags, we extract the sentence components from the 'senselabel' data table when they answer the question. We extract nouns to help us analyze, as nouns are more concrete than verbs and other sentence components, making them easier for us to understand and less abstract.

```{r load data2, warning=FALSE, message=FALSE}
cleaned_hm <- read.csv("../data/cleaned_hm.csv")
demographics <- read.csv("../data/demographic.csv")
label <- read.csv("../data/senselabel.csv")
```
```{r merge data, warning=FALSE, message=FALSE}
label_data <- label %>%
  filter(str_starts(POS, "NOUN")) %>%
  select(hmid, lowercaseLemma, POS, supersenseLabel)

label_merged <- merge(label_data, cleaned_hm, by = "hmid", all.x = TRUE)%>%
  select(hmid, wid, lowercaseLemma, supersenseLabel)
label_merged <- merge(label_merged, demographics, by = "wid", all.x = TRUE)%>%
  filter(age >= 18 & age <= 60)%>%
  filter(country=='USA')%>%
  filter(supersenseLabel != "")%>%
  mutate(lowercaseLemma = str_replace_all(lowercaseLemma, "[^[:alpha:]]", "")) %>%
  filter(lowercaseLemma != "") %>%
  select(hmid, wid, lowercaseLemma, supersenseLabel, age, gender, marital, parenthood)

label_merged$age <- as.numeric(label_merged$age)
label_merged <- label_merged %>%
  mutate(age_group = case_when(
    age >= 18 & age <= 30 ~ "18-30",
    age > 30 & age <= 60 ~ "30-60",
  ))
head(label_merged, 20)
```

  
Below is the specific implementation of the word cloud generation code, which only shows the top 80 high-frequency nouns. In subsequent word cloud generation, we will use a custom function. This word cloud displays high-frequency words related to happiness between young people (18-30) and middle-aged people (30-60). The first one is for young people, and the second one is for middle-aged people. From the word cloud, we can see that friends, work, and family are sources of happiness for both young and middle-aged people. Young people mention boyfriends and girlfriends more, while middle-aged people mention children, wives, pets, houses, and cars more.
  

```{r wordcloud age group, warning=FALSE, message=FALSE}
word_counts <- label_merged %>%
  group_by(age_group, lowercaseLemma) %>%
  summarise(count = n()) %>%
  arrange(desc(count))%>%
  select(word = lowercaseLemma, freq = count)

word_counts_teen <- word_counts %>%
  ungroup() %>%
  filter(age_group == "18-30")%>%
  select(word, freq)%>%
  head(50)
word_counts_mid <- word_counts %>%
  ungroup() %>%
  filter(age_group == "30-60")%>%
  select(word, freq)%>%
  head(50)
w1 = wordcloud2(word_counts_teen)
saveWidget(w1, "../figs/temp1.html", selfcontained = F)
w2 = wordcloud2(word_counts_mid, color='random-dark')
saveWidget(w2, "../figs/temp2.html", selfcontained = F)

if (file.exists("../figs/age_group_teen.png")) {
  img <- readPNG("../figs/age_group_teen.png")
  draw_image(img)
}else{
  webshot("../figs/temp1.html", "../figs/age_group_teen.png", delay = 20)
  img <- readPNG("../figs/age_group_teen.png")
  draw_image(img)
}
if (file.exists("../figs/age_group_mid.png")) {
  img <- readPNG("../figs/age_group_mid.png")
  draw_image(img)
}else{
  webshot("../figs/temp1.html", "../figs/age_group_mid.png", delay = 20)
  img <- readPNG("../figs/age_group_mid.png")
  draw_image(img)
}

```



The first of this pair of word clouds is about the happiness of married people, and the second is for unmarried people. Aside from their common points and some meaningless words, it can be seen that married people derive more happiness from work, family, and family members, and events like birthdays. Unmarried people, on the other hand, care more about friends, games, food, boyfriends and girlfriends, and some entertainment activities like movies.
  
```{r wordcloud marital, warning=FALSE, message=FALSE}
# Married vs. Single
generate_wordclouds("marital")
```

  

The first of this pair of word clouds is about the happiness of people with parenthood, and the second is for people without parenthood. The results here are basically consistent with those of married and unmarried people.


  
```{r wordcloud parenthood, warning=FALSE, message=FALSE}

generate_wordclouds("parenthood")
```


The first of this pair of word clouds is about the happiness of men, and the second is for women. In comparison, women mention happiness from children more frequently, while men mention it less. Men often mention games, pets, money, and some entertainment activities.

  
```{r wordcloud gender, warning=FALSE, message=FALSE}

generate_wordclouds("gender")
```
  
### Summary
This analysis, based on the HappyDB database, reveals that people's sources of happiness vary significantly based on their demographic characteristics such as age, marital status, parenthood status, and gender. The study uses data mining techniques and visualizes the results through word clouds, providing a unique perspective on what makes different groups of people happy. This information can be extremely valuable for organizations looking to boost happiness and productivity among their workers.
